Improved Bounds for Online Balanced Repartitioning

### 2020-03-29 paper/paper.tex
Sketches of 1PPL

@@

\subsection{Perfect Partition reachable within one swap}

(The version for two clusters.)

Results: LB = UB = k+1.

>>>>

\section{Perfect Partition reachable within one swap}

  (The version for two clusters, but extensions possible.)
  Results: LB = UB = k+1.

  In this section we show that the competitive ratio of the BRP variant, where the perfect partition is reachable within one swap is exactly k+1.

  Previously the best upper bound was $O(k^2)$ of DET \cite{repartition-disc}, and the best lower bound was $k-1$, utilizing the reduction from paging from \cite{repartition-disc}.
  \maciek{It is possible to improve the reduction, i.e., to reduce from paging with cache $k$, but it is impossible to have reduction from paging with cache $k+1$.}

  \begin{theorem}
    If the perfect partition is reachable within one swap, the cost of any deterministic algorithm is at least k+1.
  \end{theorem}

  \begin{proof}
    \maciek{pre-sketch}
    A request to any pair. The algorithm puts it on the wrong cluster, evicting some node and paying $1$.
    We continue to issue the requests to the evicted node (it changes every time), alg pays $k-2$.
    We issue the final request, and alg must move the initial pair, paying $2$.
  \end{proof}

  \begin{theorem}
    There exists a (k+1)-competitive algorithm for the BRP variant, where the perfect partition is reachable within one swap.
  \end{theorem}

  \begin{proof}
    \maciek{early sketch}
    The algorithm maintains components of nodes, and never splits them.
    Intially all nodes are in singleton components.
    The only choice is where to place the component, and possibly which components to evict.

  The algorithm places the first component, denoted $Z$, on an arbitrary cluster, and evicts an arbitrary node (it is a singleton).
  Consider a request $(a,b)$.
  If $a \in Z$ (also symmetry $b \in Z$), then we move the entire component $Z$ to the cluster $I(b)$, evicting a singleton node that is missplaced (i.e., is not on its initial cluster), and an arbitrary node (we later show that there exists a node that is misplaced).
  Otherwise, $I(a) = I(b)$, and we place the component there, evicting an arbitrary node (non-missplaced?).

  If a component collocated with $Z$ grows to $k-1$, we evict $Z$ and terminate.
  \end{proof}

@@
